---
title: "atble"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)
library(atbl)
```

A tibble-like package for data frames with attributes worth preserving.

## Install

Install the dev version from Github

```{r, eval = FALSE}
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}
devtools::install_github("mkearney/atbl")
```


## Usage

### Bind data frames without losing attributes

When a `data.frame` is merged with `bind_rows` (from [dplyr](https://github.com/tidyverse/dplyr)), it **loses** its attribute(s).

```{r}
bind_rows(mtcars, mtcars) %>% 
  attr("row.names")
```

When an `atbl` is merged with `bind_rows`, it **keeps** its attribute(s).

```{r}
mtcars <- as_atbl(mtcars)
bind_rows(mtcars, mtcars) %>%
  attr("row.names")
```

### Select attributes with `atselect`

Use `atselect` to select attributes the tidy way (no quotes required).

```{r}
atselect(mtcars, row.names, class)
```

### Add attributes with `add_ats`

Use `add_ats` to add one or more attributes to a data frame.

```{r}
mtcars %>%
  add_ats(seed = quote(set.seed(1234)), timestamp = Sys.time()) %>%
  attributes()
```

<!--
## Tidy evaluation reading materials

+ [Slides: Tidy Eval Hygienic FEXPRS](https://www.r-project.org/dsc/2017/slides/tidyeval-hygienic-fexprs.pdf)
+ [Thesis](https://web.wpi.edu/Pubs/ETD/Available/etd-090110-124904/unrestricted/jshutt.pdf)
+ [Blog post](http://www.onceupondata.com/2017/08/12/my-first-steps-into-the-world-of-tidyeval/)

-->
